### 2024-12-07 misc/expo/additive.tex
second convolution law

\parenproclaim Lemma {\advthm} (Convolution law). Let $Z$ is a finite abelian group and $f,g : \Z\to \CC$.
For all $\chi\in \hat Z$, we have $\hat{f*g} (\chi) = \hat f(\chi)\hat g(\chi)$.

\proof We start by expanding
$$\hat{f*g}(\chi) = \ex_{x\in Z} (f*g)(x) \bar{\chi(x)} = \ex_{x\in Z} \ex_{y+z=x} f(y)g(z)\bar{\chi(y)\chi(z)}.$$
But note that $x$ does not appear in the summand anymore, meaning that we can simply rewrite this as
an expectation
over {\it all} $y$ and $z$ (their sum will equal $x$ for some $x\in Z$). Thus we can conclude that
$$\hat{f*g}(\chi) = \ex_{y\in Z}\ex_{z\in Z} f(y)g(z)\bar{\chi(y)\chi(z)} = \hat f(\chi)\hat g(\chi),$$
which is what we wanted to show.\slug

>>>>

\parenproclaim Lemma {\advthm} (Convolution laws). Let $Z$ be a finite abelian group
and $f,g : Z \to \CC$.
For all $\chi\in \hat Z$, we have $\hat{f*g} (\chi) = \hat f(\chi)\hat g(\chi)$,
and $\hat{fg}(\chi) = (\hat f * \hat g)(\chi)$.

\proof We start by expanding
$$\hat{f*g}(\chi) = \ex_{x\in Z} (f*g)(x) \bar{\chi(x)} = \ex_{x\in Z} \ex_{y+z=x} f(y)g(z)\bar{\chi(y)\chi(z)}.$$
But note that $x$ does not appear in the summand anymore, meaning that we can simply rewrite this as
an expectation
over {\it all} $y$ and $z$ (their sum will equal $x$ for some $x\in Z$). Thus we can conclude that
$$\hat{f*g}(\chi) = \ex_{y\in Z}\ex_{z\in Z} f(y)g(z)\bar{\chi(y)\chi(z)} = \hat f(\chi)\hat g(\chi),$$
which is what we wanted to show.

To prove the other convolution law, we instead expand
$$\eqalign{
(\hat f * \hat g)(\chi) &= \sum_{\psi \in \hat G} \hat f(\psi) g(\chi\psi^{-1})  \cr
&= \sum_{\psi\in \hat G} \ex_{x\in G}f(x)\bar{\psi(x)}\ex_{y\in G} g(x+y) \bar{\chi(x+y)\psi^{-1}(x+y)} \cr
&= \ex_{x\in G} f(x) \ex_{y\in G} g(x+y) \bar{\chi(x+y)} \sum_{\psi\in \hat G} \bar{\psi^{-1}(y)}.\cr
}$$
The innermost sum equals $|\hat Z|$ when $y=0$ and is $0$ otherwise. Hence
$$\eqalign{
(\hat f * \hat g)(\chi) &= \ex_{x\in G} f(x) \ex_{y\in G} g(x+y) \bar{\chi(x+y)} \one_{[y=0]} |\hat Z| \cr
&= \ex_{x\in G} f(x) g(x) \bar{\chi(x)} \cr
&= \hat{fg}(\chi), \cr
}$$
which is what we wanted to show.\slug
